---
title: "fuzzer-results"
author: "Pierre Donat-Bouillud"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, root.dir = normalizePath(".."))

library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(fst)
library(DT)
library(stringr)

here::i_am("notebooks/merge-performance.Rmd")
library(here)
```

## Loading data

```{r}
sig_baseline <- as_tibble(read_fst("/mnt/ocfs_vol_00/signatr/run_existing-5.fst"))
sig_fuzz <- as_tibble(read_fst("/mnt/ocfs_vol_00/signatr/run_fuzz-5.fst"))
```

# First look

```{r}
n_sig_baseline <- sig_baseline %>% filter(is.na(warnings), !is.na(signature)) %>% pull(signature) %>% n_distinct()
n_sig_fuzz <- sig_fuzz %>% filter(is.na(warnings), !is.na(signature)) %>% pull(signature) %>% n_distinct()
```

There are `r n_sig_baseline` distinct signatures of calls without warnings for the baseline, and `r n_sig_fuzz` for the fuzzed calls.

## Per function

```{r}
sig_base_func <- sig_baseline %>% filter(!is.na(signature)) %>%  group_by(pkg_name, fun_name) %>% summarize(n_sigs = n_distinct(signature))
sig_fuzz_func <- sig_fuzz %>% filter(!is.na(signature)) %>%  group_by(pkg_name, fun_name) %>% summarize(n_sigs = n_distinct(signature))

n_sig_diff <- left_join(sig_base_func, sig_fuzz_func, by = c("pkg_name", "fun_name"), suffix=c("_base", "_fuzz"))
```


Functions for which fuzzing finds less signatures:
```{r}
n_sig_diff %>% filter(n_sigs_base > n_sigs_fuzz)
```

Functions for which it finds more:

```{r}
more_sigs <- n_sig_diff %>% filter(n_sigs_base < n_sigs_fuzz)
more_sigs %>% mutate(ratio = n_sigs_fuzz / n_sigs_base) %>% ungroup() %>% summarise(me = mean(ratio), med = median(ratio), sd = sd(ratio) )
```

## What is a high quality type signature?

If there is an error or a crash, we do not get a type signature.

But what about warnings? And messages? Can we classify them?

### Warnings

```{r warnings}
sig_warnings <- sig_fuzz %>% filter(!is.na(warnings)) %>% mutate(warns = str_split(warnings, fixed(";"))) %>%  summarize( warnings_c = do.call(c, warns)) %>% count(warnings_c, sort = TRUE)  %>% mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))
sig_warnings
```

We can try some heuristics: coercion messages will have the form of _coercing_ or _should be_, or indication that `NA` or `NaN` were produced.

1. Should be

```{r}
should_be <- sig_warnings %>% extract(warnings_c, into = c("arg_name", "type"), "argument `([^`]+)` should be (.*)") %>% filter(!is.na(arg_name) | !is.na(type))
should_be
```

2. _is.na() applied to non-(list or vector) of type_

```{r}
is_na_type <- sig_warnings %>% extract(warnings_c, into = c("given_type"), "is.na\\(\\) applied to non-\\(list or vector\\) of type (.*)") %>% filter(!is.na(given_type))
is_na_type
```

3. Coercing

```{r}
coercing_to <- sig_warnings %>% extract(warnings_c, into = c("arg_name", "coercing_type"), "Coercing `([^`])*` to (.*)") %>% filter(!is.na(coercing_type))
coercing_to
```


```{r}
sig_warnings %>% filter(str_detect(warnings_c, "(C|c)oerci(ng|on)"))
```

_longer argument not a multiple of length of shorter_; _data length [5] is not a sub-multiple or multiple of the number of rows [2]_ : this error message suggests a numeric relation between two arguments.

### Messages

```{r messages}
sig_fuzz %>% filter(!is.na(messages)) %>% count(messages, sort = TRUE) 
```

Most of them are about loading a library. We can ignore them.

# Feedback

In addition to warnings, we can also use the errors.

```{r errors}
sig_errors <- sig_fuzz %>% filter(!is.na(error)) %>% mutate(errs = str_split(error, fixed(";"))) %>%  summarize( errors_c = do.call(c, errs)) %>% count(errors_c, sort = TRUE)  %>% mutate(pc = 100 * n / sum(n), cpc = cumsum(pc)) 
sig_errors
```

1. _must be_

```{r}
must_be <- sig_errors %>% extract(errors_c, into = c("arg_name", "type"), "`([^`])*` must be (.*)") %>% filter(!is.na(type))
must_be
```

And if it is an enumeration of types?

```{r}
# actually only the 1st two and it will not correctly detect types with spaces inside
all_types <- must_be %>% pull(type) %>% str_match("(?:either )?a ([:alnum:]*)(?: or a ([:alnum:]*))?")
all_types[apply(all_types, 1, function(row) { !is.na(row[2])}),]
```


We can further extract the multiple option _one of_:

```{r}
must_be %>% extract(type, into = "options", "one of (.*)") %>% filter(!is.na(options))
# TODO: extract all the possible options there
```


2. _cannot be coerced to_

```{r}
sig_errors %>% filter(str_detect(errors_c, fixed("cannot be coerced")))
```


3. _stopifnot errors_

```{r}
sig_errors %>% filter(str_detect(errors_c, fixed("is not TRUE")))
```


Then we can detect the presence of type checking functions, such as `is.integer` and so on...


## Return metadata


## Type stability

Does the return type of the function change often? How?

```{r}
get_return_type <- function(sig) {
  str_match(sig, ".* -> (.*)")[,2]
}

sig_fuzz_ret <- sig_fuzz %>% mutate(ret_type = get_return_type(signature))
```


```{r}
sig_fuzz_ret %>% filter(!is.na(signature)) %>% group_by(pkg_name, fun_name) %>% summarize(n_return_types = n_distinct(ret_type), ret_types = paste0(unique(ret_type), collapse = "; "))  %>% filter(n_return_types > 1)
```
What are the functions which have several return types but one that is seldom used?

```{r}
sig_fuzz_ret %>% filter(!is.na(signature)) %>% group_by(pkg_name, fun_name) %>% count(ret_type) %>% mutate(n_return_types = n_distinct(ret_type)) %>% arrange(desc(n_return_types))  %>% filter(n_return_types > 1, n_return_types < 10, any(n == 1), any(n > 1)) 
```

